A Guide to Pre-Processing High-Throughput Animal Tracking Data

### 2021-02-04 docs/ms_atlas_preproc_main_text.tex
more listing edits

\begin{lstlisting}[float, language=R, style=customR, caption = {
    Removing prolonged spikes from a movement track. 
    The important function arguments here are \texttt{point\_angle\_cutoff} ($A$), \texttt{reflection\_speed\_cutoff} ($S$), and \texttt{est\_ref\_len}, the maximum number of positions after the inner bound that are candidates for the end of the prolonged spike, i.e., the outer bound. 
    If the prolonged spike ends after less than $N$ positions, the true end point is used as the outer bound of the spike.
    However, the algorithm behind this function fails when the prolonged spike ends after more than $N$ positions. 
    Users are advised to use a liberally large value of N in the \texttt{est\_ref\_len} argument; 1,000 may be appropriate for 3s interval data.
    Further, users are cautioned against relying on such algorithms for severely distorted data.}]
filtered_data <- atl_remove_reflections(data = track_data,
                       x = "x", y = "y", time = "time",
                       point_angle_cutoff = A,
                       reflection_speed_cutoff = S,
                       est_ref_len = N)
\end{lstlisting}

>>>>

% \begin{lstlisting}[float, language=R, style=customR, caption = {
%     Removing unrealistic movement in the form of prolonged spikes from a movement track. 
%     The important function arguments here are \texttt{point\_angle\_cutoff} ($A$), \texttt{reflection\_speed\_cutoff} ($S$), and \texttt{est\_ref\_len}, the maximum number of positions after the inner bound that are candidates for the end of the prolonged spike, i.e., the outer bound. 
%     If the prolonged spike ends after less than $N$ positions, the true end point is used as the outer bound of the spike.
%     However, the algorithm behind this function fails when the prolonged spike ends after more than $N$ positions. 
%     Users are advised to use a liberally large value of N in the \texttt{est\_ref\_len} argument; 1,000 may be appropriate for 3s interval data.
%     Further, users are cautioned against relying on such algorithms for severely distorted data.}]
% filtered_data <- atl_remove_reflections(data = track_data,
%                        x = "x", y = "y", time = "time",
%                        point_angle_cutoff = A,
%                        reflection_speed_cutoff = S,
%                        est_ref_len = N)
% \end{lstlisting}
